Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-10 thesis/abstract.tex
Proof read updates

\vskip.35in
{\large Andrew J. Emerick} \\
\vskip.35in
\end{center}
Motivated by the desire to better understand two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
%In this \thesis
we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and the multi-channel stellar feedback and multi-element metal yields associated with each star. We developed these simulations as a means to better understand the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies. We follow the evolution of the individual metal yields associated with these stars in order to better understand how metals mix within the ISM and are ejected into the circumgalactic and itergalactic media (CGM, IGM) through outflows. This study is directed with the goal of better understanding the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies.

>>>>

\vskip.35in
{\large Andrew J. Emerick} \\
\vskip.35in
\end{center}
Motivated by the desire to better understand two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
%In this \thesis
we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and the multi-channel stellar feedback and multi-element metal yields associated with each star. We developed these simulations as a means to better understand the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies. We follow the evolution of the individual metal yields associated with these stars in order to better understand how metals mix within the ISM and are ejected into the circumgalactic and intergalactic media (CGM, IGM) through outflows. This study is directed with the goal of better understanding the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies.
